---
title: "Assignment1"
author: "Chia-Hao Lo"
date: "September 28th 2024"
output:
  pdf_document: default
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```

```{r }
#Load the required packages
library(tidyverse)
library(inspectdf)
library(caret)
library(moments)
library(tidymodels)
library(modelr)
library(ISLR)
library(car)
```

# Q1. Loading the data

We need to calculate our ysn to satisfy the delivery specification

```{r}
# Your student number goes here
ysn = 1907385
# Calculate your student number modulo 3
mod4 <- ysn %% 4
mod4
```

[After calculating ysn we get 1. Due to deliverable specification that ysn = 1 mod 4 use the Indian data, we will use Indian data as our dataframe]

```{r}
filename <- paste0("a1_1907385_3", ".pdf")
filename

# Read in the data using the correct tidyverse command

ind1 <- read_csv("./data/India.csv")
ind1 <- as_tibble(ind1)

# Display the first 10 lines of the data
head(ind1, 10)
```

# Q2. The dimensions of the data set

For this part, we will use dim() function to get a list of the form.

```{r}
#Dimension
dim(ind1)
```

The dimensions of the data frame is [50 rows, 8 columns]


# Q3. Random permutation of the rows


From the delivery specification, we know seed equals to ysn, we gt ysn from Q1 and ysn = 1. Then we permute all rows into data set.
```{r}
#
set.seed(ysn)
ind1_permuted <- sample_n(ind1, 50)
head(ind1_permuted, 10)
```

The result shows the first 10 rows.

# Q4. Adding an extra column of row numbers

We add new rows and use relocate() to set this row to the first row.

```{r}
#
ind1_permuted1 <- ind1_permuted %>%
  mutate(Rows = row_number()) %>% relocate("Rows", .before = Player)

head(ind1_permuted1, 10)
```


# Q5 Data cleaning

Here we test if the data set contains the duplicated data.
```{r}
# Check if the data has some duplicated rows
ind1_clean <- ind1_permuted1 %>%
  distinct()
sum(duplicated(ind1_clean))
```
Here we delete test data
```{r}
ind1_clean1 <- ind1_clean %>%
  filter(!(Player == "test1test1")
         )
```

Here we convert negative data to positive data.
```{r}
#To get absolute value for whole data
ind1_clean1[ind1_clean1$Player == "IK Pathan", "2005"] <- 
  str_replace(ind1_clean1[ind1_clean1$Player == "IK Pathan", "2005"], "-", "")
ind1_clean1
```
Here we detect if here is any NA data.
```{r}
#To check if there is any missing values in any columns
inspect_na(ind1_clean1)
```
Here we need to convert word zero to number 0
```{r}
ind1_clean2 <- ind1_clean1 %>%
  mutate(`2002` = str_replace(`2002`, "zero", "0"))
print(ind1_clean2[ind1_clean2$Player == "T Yohannan", "2002"])
```
Delete player NM Kulkarni row because in 2001 data is impossible for one innings to get 9999 runs.
```{r}
ind1_clean3 <- ind1_clean2 %>%
  filter(!(Player == "NM Kulkarni")
  )

print(ind1_clean3 %>% filter(Player == "NM Kulkarni"))
```

To find the values in RightHanded column that is not yes or no
```{r}
invalid_values <- ind1_clean3[!(ind1_clean3$RightHanded %in% c("yes", "no")),]
invalid_values
```
Here we found out there are two rows need to fix. First we change rows in RightHanded column contain Y to yes, like other data.
```{r}
#Change Y to yes
ind1_clean3$RightHanded[ind1_clean3$RightHanded == "Y"] <- "yes"
ind1_clean3
```
After we look at this row we know this row is test row and there is no valued data. So we will remove it.


After cleaning the database, we start to tidy the data. First, we convert 2000-2005 columns to two new columns year and performance.


# Q6 Tidy data
# (a)
```{r}
ind1_convert <- ind1_clean3 %>%
  gather(key = "year", value = "performance", starts_with("200"))

ind1_convert
```
Here we separate the performance to four new columns.


# (b)
```{r}
details <- str_match(ind1_convert$performance, "(\\d+) innings, (\\d+) outs, (\\d+) runs, (\\d+) balls")
ind1_performance <- ind1_convert %>%
  mutate(
    Innings = as.numeric(details[,2]),
    Outs = as.numeric(details[,3]),
    Runs = as.numeric(details[,4]),
    Balls = as.numeric(details[,5])
  )
ind1_performance
```
After we get four new columns then we can delete performance column.


# (c)
```{r}
ind1_cleaned <- ind1_performance %>%
  select(-performance)
ind1_cleaned
```
Here we add T_rows with the row numbers


# (d)
```{r}
ind1_cleaned1 <- ind1_cleaned %>%
  mutate(T_rows = row_number()) %>%
  relocate(T_rows, .before = Player)
head(ind1_cleaned1, 10)
```

# Q7 Data types
.Rows: Categorical Ordinal(each row number follows the order and it is for category the order of the players)

.T_rows: Categorical Ordinal(each row number follows the order and it is for category the order of the rows)

.Player: Categorical Nominal(names of player, which are labels also no natural order for player names)

.RightHanded: Categorical Nominal(it shows if the player is righthanded, this is a categorical nominal variable, which is yes or no)

.year: Categorical Ordinal(represents a sequence of time)

.Innings:Quantitative Discrete(the counts of innings played in a given year)

.Outs:Quantitative Discrete(counts how many times a player was out)

.Runs:Quantitative Discrete(total scores of runs scored by a player)

.Balls:Quantitative Discrete(certain counts of a player faced the total number of balls)

# Q8 Tame data
Here we will follow Tame data from my uni material steps, first we lower case, then we convert the data type to question 7 data type we found.
```{r}
ind1_taming <- ind1_cleaned1 %>%
  rename_with(tolower)

ind1_taming$rows <- as.ordered(ind1_taming$rows)

ind1_taming$t_rows <- as.ordered(ind1_taming$t_rows)

ind1_taming$year <- as.ordered(ind1_taming$year)

ind1_taming$player <- as.factor(ind1_taming$player)
head(ind1_taming, 10)
```

```{r}
dim(ind1_taming)
```
Here we filter the data is non-zero, we remove the balls are equal to zero


# Q9 Non-zero ball data
```{r}
ind1_balls <- ind1_taming %>%
  filter(balls > 0)
head(ind1_balls, 10)
```
```{r}
dim(ind1_balls)
```
Here we set the correct seed again and set 70 rows


# Q10 Random subset
# (a)
```{r}
set.seed(ysn)
ind1_sample <- sample_n(ind1_balls, 70)
```
Here we sort the rows by tidy row numbers
# (b)
```{r}
ind1_sorted <- ind1_balls %>%
  arrange(t_rows)
head(ind1_sorted, 10)

```

```{r}
dim(ind1_sorted)
```
Here we calculate the percentage of innings and he number of runs scored per ball, then change two columns' location


# Q11 pct_out & run_rate
# (a)
```{r}
ind1_new_columns <- ind1_sorted %>%
  mutate(
    pct_out = round((outs/innings)*100, 2),
    run_rate = round(runs/balls, 3)) %>% 
  relocate(pct_out, run_rate, .after = year)
#head(ind1_new_columns, 10)
ind1_new_columns
```
.pct_out: Quantitative Continuous(this is a numeric and presents by percentage)

.run_rate: Quantitative Continuous(this represents the runs score per ball and it can be any numeric value)
```{r}
dim(ind1_new_columns)
```

# (b)
For the percentage of outs, it is calculate outs/innings, it is the same as pct_out. Thus we use min() function to find the lowest percentage of outs.
```{r}
min_pct_out = ind1_new_columns %>%
  filter(pct_out == min(pct_out)) %>%
  select(player, year, pct_out)
min_pct_out
```
From the results, there are 6 players with the lowest percentage of outs, which are same value of 0 %.

We need to find the highest run rate, which is run_rate's dataset. We use max() function to find the highest value.
```{r}
max_run_rate <- ind1_new_columns %>%
  filter(run_rate == max(run_rate)) %>%
  select(player, year, run_rate)
max_run_rate
```
For the highest run rate, the result shows in 2001, and the value is 0.967.

Here we change the year data type and perform the boxplot


# Q12 Boxplot using year
```{r}
ind1_new_columns1 <- mutate(ind1_new_columns, year = factor(year, ordered = TRUE))

ggplot(ind1_new_columns1, aes(x = year, y = run_rate, fill = righthanded)) +
  geom_boxplot()
```
Here we also perform two boxplots


# Q13 Side-by-side boxplots
```{r}
boxplot_pct_out <- ggplot(ind1_new_columns1, aes(x = righthanded, y = pct_out, fill = righthanded)) +
  geom_boxplot()

boxplot_pct_out
```

```{r}
boxplot_run_rate <- ggplot(ind1_new_columns1, aes(x = righthanded, y = run_rate, fill = righthanded)) +
  geom_boxplot()
boxplot_run_rate
```


# Q14 Analysis
Based on the analysis in Q11, we found that players with a lower percentage of outs (pct_out) generally perform blanded. For example, T Yohannan had the lowest percentage of outs at 0%, his data mostly is 0 and it means he has lower priority playing rate. In contrast, players with a higher percentage of outs were more likely to have higher run rates, as their innings were higher.

In the box plots, we can see the patterns based on handedness. right-handed players had a wider variation in run_rate across years compared to left-handed players. For example, in the year 2004, right-handed players had a significantly higher spread in run_rate. For left-handed players showed more consistency, like 2002, the run_rate distribution was more compact.

Additionally, the box plots of pct_out and run_rate by handedness shows right-handed players seemed to perform better on average, as shown by a higher median run_rate and a generally lower pct_out. This suggests that right-handed players may have an advantage or perhaps more opportunities in the dataset used.
